Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-18 ms.tex
planet properties words

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine ground-based seeing limited survey data and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
orbital period of 33 days.
We also present \texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
for \KT\ candidates.
\end{abstract}

@@

\dfmtodo{Re-write this section.}
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

@@

(Include comment here about how the planet parameters assume no dilution.
Except for the two that we have AO detected binaries for, probably?
Brendan should have us flux ratios by the end of the day.
In those cases, I suppose we need to include planet properties in both cases
in which the transit is around either the more or less massive star.)

@@

\subsection{Adaptive Optics Imaging}

@@

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
Instead, it is at an reduced semimajor axis \ars$ = 82.1 \pm 8.6$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 275 \pm 15$
K, meaning its bulk insolation is $135 \pm 30$ percent that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14},
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by
\kep.

>>>>

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine ground-based seeing limited survey data and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a $2.29 \pm 0.24 R_\odot$ planet with $T_{eq} = 273 \pm 15$ K and an
orbital period of 33 days.
We also present \texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
for \KT\ candidates.
\end{abstract}

@@

In \paperit, we present only parameters directly observable from the \KT\
light curve itself: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.

For each candidate, we fit a transit and systematic model simultaneously
to the data.
The transit model is an exposure-time integrated, two-parameter limb darkened 
light curve \citep{Mandel02,Kipping10b}.
We parameterize... \dfmtodo{What are the parameters in the model?}

This method enable us to marginalize over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

@@

\dfmtodo{Add more to this section.}

In this analysis, we assume the dilution caused by additional stars contributing
flux into the aperture is negligible for nearly all systems.
Given the location of the \Ci\ field at a high galactic latitude, we expect low
contamination by background giants. 
Nevertheless, this assumption may not be valid for all systems.
Any contamination unaccounted for, as may happen if any of these stars are
actually unresolved binaries, would cause us to underestimate the radii
of any planets we detect.
Therefore, high-contrast adaptive optics imaging of any systems should be
obtained before any of these planets are placed on a planet mass-radius
diagram.

One system, EPIC 201828749, is known to be a binary through AO imaging
as discussed in \ref{sec:AO}. \btmtodo{More text...}

@@

\subsection{Adaptive Optics Imaging}
\label{sec:AO}

@@

Unlike GJ\,1214b, EPIC 201912552b is not highly irradiated.
Instead, it is at an reduced semimajor axis \ars$ = 83.2 \pm 9.1$.
Its equilibrium temperature is then, assuming zero albedo, $T_{eq} = 273 \pm 15$
K, meaning its bulk insolation is $131 \pm 30$ percent that of the Earth's.
Although the planet is likely too large to be rocky \citep{Rogers14},
its atmosphere is likely to be the focus of many future observations, providing
a cool analogue to the highly irradiated planets of a similar size found by
\kep.
